{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2020-08-12 documents/pamphlet.tex
Coplanar amp

This is a condensed version of a (horribly unfinished) paper at \href{https://www.github.com/0xDBFB7/covidinator/documents/paper.pdf}{\faGithub/0xDBFB7/covidinator}.\footnote{Daniel Correia [TODO: affiliation] \orcidlink{0000-0002-9353-0216}}

@@

@@

\cite{Microwave2009} \textrightarrow \ (\cite{focusing2014} $\parallel$ \cite{Efficient2015} $\parallel$ \cite{Resonant2017})\footnote{A great many papers are involved.} appear to establish that the net charge, mass distribution, and envelope stiffness of a few species of viruses support a weak resonance mode in the microwave spectrum, with a peak at roughly 8 GHz for Inf. A.

@@

However, this work would seem to be more useful if extended with the following assertion: the virus' Q factor is only about 2, meaning that the steady-state amplitude and stresses should be reached in some nanoseconds.

Barring protein mechanical fatigue \cite{Mechanical2013} or some other mechanism that could prolong the inactivation duration, it appears to be possible to reduce the required power density to a minuscule fraction of all safety limits by pulsing the field at nanosecond scales. This incidentally allows scanning of a focal point, a significant area can be treated with a relatively small transmit power.

\cite{Efficient2015} test with various strains of Influenza A, we are testing with Coliphage T4; structural similarities with NCoV mean this is may be transferable.

@@

\begin{autem}
	It should be noted that all of the claims we make hinge on this nanosecond inactivation. \cite{Efficient2015} and \cite{focusing2014} use a 15-minute exposure, which is apparently the norm for this field. 
\end{autem}

@@

From crude attenuation data, this pulsed field can be safely produced at least 3 cm deep in tissue. This would seem to be unlike any other mechanisms like near or far\cite{Germicidal2017}UV. suitable for targeted sterilization of with bronchoscopic techniques), opening up a particularly interesting direct treatment modality. We are trying to verify this now with FDTD sims.

@@

@@

\clearpage 
{\Large \textbf{How do we wield this sword?}}

This is not a particularly demanding requirement, and lends itself to a wide variety of applications, many of which could be implemented almost immediately.

On an individual level, the free-space-combined output of, say, a few dozen SiGe:C or GaAs transistors (\$0.3 apiece [BFP620]), very similarly to our reference design, should suffice to locally protect the major vulnerabilities like mouth, nose, eyes, hair and any surfaces that the hands contact. This arguably wouldn't provide many advantages over simple masks, however.

@@

>>>>

This is a condensed version of a (horribly unfinished) paper at \href{https://www.github.com/0xDBFB7/covidinator/documents/paper.pdf}{\faGithub/0xDBFB7/covidinator}.\footnote{Daniel Correia [TODO: affiliation] \orcidlink{0000-0002-9353-0216}} A paltry few more details and a bibliography are available therein.

@@

\begin{figure}[H]
	\includegraphics[width=\textwidth]{../media/eppenwolf.jpg}
	\caption{Failure is just success rounded down.}
\end{figure}

@@

\cite{Microwave2009} \textrightarrow \ (\cite{focusing2014} $\parallel$ \cite{Efficient2015} $\parallel$ \cite{Resonant2017})\footnote{A great many more papers are involved.} appear to establish that the net charge, mass distribution, and envelope stiffness of a few species of viruses support a weak resonance mode in the microwave spectrum, with a peak at roughly 8 GHz for Inf. A.

@@

However, this work would seem to be more useful if extended with the following assertion: the virus' Q factor has been determined to be only about 2, meaning that the steady-state amplitude and stresses should be reached in some nanoseconds.

Barring protein mechanical fatigue \cite{Mechanical2013} or some other mechanism that could prolong the inactivation duration, it appears to be possible to reduce the required dissipated energy density to a minuscule fraction of all safety limits by pulsing the field at nanosecond scales. This incidentally also permits scanning of a focal point so that a significant area can be treated with a relatively small transmit power.

\cite{Efficient2015} test with various strains of Influenza A, we are testing with Coliphage T4; structural similarities with NCoV mean this may be transferable.

@@

\begin{autem}
	It should be noted that all of the claims we make hinge on this hypothesis of nanosecond-scale inactivation. \cite{Efficient2015} and \cite{focusing2014} use a 15-minute exposure, which is apparently the norm for this field. We are trying to obtain data to more firmly establish this now.
\end{autem}

@@

From crude attenuation data, this pulsed field can be safely produced at least 3 cm deep in tissue. This would seem to be unlike any other mechanisms in its specificity; near or far\cite{Germicidal2017}UV, chemical sterilization, etc. This opens up a particularly interesting direct treatment modality.

@@

Equally unlike other techniques, if the assumptions above hold, this would act instantaneously, providing $>$ 80\% inactivation in the targeted area (depending on some population parameters).

The amplifiers for this frequency range fall within the regime of many off-the-shelf radar systems; miniature personal emitters could be produced for $ < \$10$ with semiconductor amplifiers; and the high-power systems for direct treatment are only a few orders of magnitude above that.

@@

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{biology/output_35_1.png}
\end{figure}

### 2020-08-12 documents/supplemental.tex
Coplanar amp

>>>>

Much of this project was done in 1.5 mm microstrip with a 2.5 to 3 mm routed isolation. However, it became apparent that the inductance of vias with the ground plane was too great. It has been suggested that low-inductance vias in prototypes \cite{Microwavee}

Grounded coplanar waveguide, where the primary ground plane is on the top side of the board, presents many advantages, and in later testing appeared to provide much better performance. connectors can interface with the top side; the sizes are much more compatible with small SMD devices.
